---
title: "Drug Efficiency for Everyone"
author: "Kwincy Little"
date: "December 2019"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

a new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. Finish this!

# Methods
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->
Our two variable of interest is treatment and infected. For this section we will be using the data called avast, which includes everyone. Both factor variables categorical. For this project we will be using a barchart for the graphical results and a xtab command for the numerical results. 

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results
It shows that the percentage of people who got aids and was taking the drug are lower than those who took the placebo. By the looks of the barchart the drug seems to be working.

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected + treatment,data=avast,type="percent",main="Drug Efficiency for Everyone")
```

By the looks of the the barchart, the drug seems to be working. It is that the percentage of people who got aids and was taking the drug are lower than that of those who took the placebo. 


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~infected + treatment, data=avast)
rowPerc(table1)
colPerc(table1)
```
The numerical results show that the drug seems to be very effective for at preventing aids. About 41% percent of those who took the drug got aids and about 59% of those who took the placebo got aids, that means the drug was effective at preventing aids since the percentage of those who took the drugs and got aids is low. 


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
chisq.test(table1)
chisqtestGC(table1)
```
The p value for this chi square test is 2.2e-16, which is less than our threshold of belief of .05. Since our p value is less than .05, we could reject the null hypothesis, but we still need to evaluate the fisher test.

```{r}
fisher.test(table1)
```


# Discussion and Conclusion
<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Our p value is 2.2e-16 for the chi square test and 2.333e-07 for the fisher test. This means the probability of getting a sample like this under conditions when the null hypothesis is true is about 0%. Our p value is less than our threshold of belief which is .05 (five percent). Since the p value is less than .05, we reject the null hypothesis and conclude that there is a difference between taking the drug or taking the placebo and getting aids for everyone. This data shows that taking the drug is effective in preventing aids for everyone. This data also indicates that taking the drug has a positive effect for everyone. 
